Turbulence in compact to giant H~II regions

### 2023-05-09 strucfunc_paper.tex
Minor changes to Javier's text on error bars. Ready to resubmit!

For the observational values (\(B\obs(r)\); blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
%The uncertainty of each bin (blue error bars) is estimated
%as the standard deviation of these values divided by the square root of
%the number of contributing pairs.
\NEW{The uncertainty of each bin (blue error bars) is estimated
as the fractional error of the respective \(B\obs(r)\) value.
These values are indicated in the third column of the table given in the Appendix D. 
In the same table, the forth and fifth columns show, as multiples of their respective fractional error, additional weight at small and large scales. 
This is the case for the EON, and the regions observed using the FLAMES and the TAURUS instruments.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).

>>>>

For the observational values (\(B\obs(r)\); blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
%The uncertainty of each bin (blue error bars) is estimated
%as the standard deviation of these values divided by the square root of
%the number of contributing pairs.
\startNEW
We judge the dominant source of error in \(B\obs(r)\) to be systematic,
rather than random, so we set the uncertainty of each bin (blue error bars)
as a constant fraction (2 to 8\%) of the observed value,
as listed in column 3 of Table~D1 (see supplementary material).
In some sources
(EON, and the regions observed using the FLAMES and the TAURUS instruments)
the uncertainty is increased by a factor of order two for a small number of bins
at the smallest and largest scales (columns 4 and 5 of Table~D1).
\stopNEW
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
